Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-08 edubots_surveys.Rnw
reviewed conclusions - par 5-7

% No remarkable differences between different groups.
This introduction of chatbots and chatbot technology will be helped by the fact
that no discernible differences are found between different groups. Even if
chatbots do have some potential for personalization or customization, based on
the class material, student and teaching staff, the general introduction of the
technology can be done in a general way and for all disciplines, teaching
experience and gender.

At any rate, the general feeling that transpires from the survey is that it is
essential for any institution to take into account the shareholder's opinion
when introducing chatbots. This is true almost across the board, but in the case
of chatbots (and instant messaging applications) their immediacy and the fact
that they can enter into what we could call the private sphere makes this even
more necessary.

One of the questions we made in the {\bf second survey}, related to
the messaging applications used by tertiary education teachers, opens a new line
of inquiry about what they {\em perceive} as such, and about how it is used.
Namely, the responses indicated that the teachers perceived as messaging
application not only what is usually called a chat or instant messaging app such
as WhatsApp or Microsoft Teams, but also the means provided by the university for
communicating with the student, such as a feature of grading applications that
will email the grade to the student. This implies that there is a need by
teachers, communication with students, also mostly unidirectional, and that it
does not matter so much how that need is covered. However, this will need careful
consideration, including how it ties with the automation of the learning
experience that the chatbots bring.

>>>>

% No remarkable differences between different groups.
The introduction of chatbots and chatbot technology will be helped by the fact
that no discernible differences are found between different groups. Even though
chatbots do have some potential for personalization or customization based on
the class material, student, and teaching staff, the general introduction of the
technology can be done in a general way and for all disciplines, teaching
experience, and gender.

Overall, the general feeling that transpires from the survey is that it is
essential for any institution to take into account shareholders' opinions
when introducing chatbots. This is true almost across the board, but in the case
of chatbots (and instant messaging applications) their immediacy and the fact
that they can enter into what we could call the private sphere makes this even
more necessary.

One of the questions in the {\bf second survey}, which asked about 
the messaging applications used by tertiary education teachers, opens a new line
of inquiry about what teachers {\em perceive} as such, and how it is used.
Namely, the responses indicated that teachers perceived as messaging
application not only traditional chats or instant messaging app such
as WhatsApp or Microsoft Teams, but also the means provided by their university for
communicating with students, such as a feature of grading applications that
emails grades to students. This suggests that teachers have a need for communication with students, 
which is mostly unidirectional, and that it
does not matter as much how that need is met. However, this will need careful
consideration, including how it ties with the automation of the learning
experience provided by chatbots.
